The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-15 paper/mri_paper.tex
hmri equations

Following the same prescription for weakly nonlinear tuning, multiscale expansion, and perturbation expansion, we find the equations for the HMRI up to order $epsilon^3$.

@@

\mathcal{L} \mathbf{V_1}

>>>>

Following the same prescription for weakly nonlinear tuning, multiscale expansion, and perturbation expansion, we find the equations for the HMRI up to order $\epsilon^3$.

@@

\beq
\mathcal{L} \mathbf{V_1} + \xi B_0 \mathcal{H} \partial_z \mathbf{V_1} = 0
\eeq

\beq
\mathcal{L}\mathbf{V_2} = \mathbf{N_2} - \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1} + \xi \mathcal{H} \partial_z \mathbf{V_2} - \xi \mathcal{H}\partial_Z \mathbf{V_1}
\eeq

\begin{multline}
\mathcal{D}\partial_T \mathbf{V_1} \, + \, \mathbf{N_3} \, = \, \mathcal{L} \mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} \, \\
- \partial_z\mathcal{X}\mathbf{V_1} \, - \partial_z^3\mathcal{L}_3\mathbf{V_1} + \xi \mathcal{H} \partial_z \mathbf{V_3} - \xi \mathcal{H} \partial_Z \mathbf{V_2} + \xi \mathcal{H} \partial_z \mathbf{V_1}.
\end{multline}
